\begin{thebibliography}{99}

\bibitem{Detectors for Dark Matter search (Review)}
Akimov D. Detectors for Dark Matter search (Review) // Nucl. Instrum. Meth. A. 2009. Vol. 598. P. 275. 

\bibitem{Advances in Cryogenic Avalanche Detectors}
Buzulutskov A. Advances in Cryogenic Avalanche Detectors // J. of Instrumentation. 2012. Vol. 7. C02025. 

\bibitem{Liquid Noble Gas Detectors for Low Energy Particle Physics}
Chepel V., Araujo H. Liquid Noble Gas Detectors for Low Energy Particle Physics // J. of Instrumentation. 2013. Vol. 8. R04001. 

\bibitem{New Results from DAMA/LIBRA}
Bernabei R. et al. New Results from DAMA/LIBRA // Eur. Phys. J. C. 2010. Vol. 67. P. 39. 

\bibitem{CoGeNT: A Search for Low-Mass Dark Matter using p-type Point Contact Germanium Detectors}
Aalseth C. E. et al. CoGeNT: A Search for Low-Mass Dark Matter using p-type Point Contact Germanium Detectors // Eprint arXiv:1208.5737. 2012.

\bibitem{Results from 730 kg Days of the CRESST-II Dark Matter search}
Angloher G. et al. Results from 730 kg Days of the CRESST-II Dark Matter search // Eur. Phys. J. C. 2012. Vol. 72. P. 1971. 

\bibitem{Dark Matter Search Results Using the Silicon Detectors of CDMS II}
Agnese R. et al. Dark Matter Search Results Using the Silicon Detectors of CDMS II // Eprint arXiv:1304.4279. 2013. 

\bibitem{Search for Light Dark Matter in XENON10 Data}
Angle J. et al. Search for Light Dark Matter in XENON10 Data // Phys. Rev. Lett. 2011. Vol. 107. 051301. 

\bibitem{Dark Matter Results from 225 Live Days of XENON100 Data}
Aprile E. at al. Dark Matter Results from 225 Live Days of XENON100 Data // Phys. Rev. Lett. 2012. Vol. 109. 181301.

\bibitem{WIMP-Nucleon CrossSection Results from the Second Science Run of ZEPLIN-III}
Akimov D. et al. WIMP-Nucleon CrossSection Results from the Second Science Run of ZEPLIN-III // Phys. Lett. B. 2012. Vol. 709. P. 14.  

\bibitem{Two-Phase Emission Detector for Measuring Coherent Neutrino-Nucleus Scattering}
Hagmann C., Bernstein A. Two-Phase Emission Detector for Measuring Coherent Neutrino-Nucleus Scattering // IEEE Trans. Nucl. Sci. 2004. Vol. 51. P. 2151. 

\bibitem{Detection of Reactor Antineutrino Coherent Scattering off Nuclei with a Two-Phase Noble Gas Detector}
Akimov D. et al. Detection of Reactor Antineutrino Coherent Scattering off Nuclei with a Two-Phase Noble Gas Detector // J. of Instrumentation. 2009. Vol. 4. P06010. 

\bibitem{Comments on "First Dark Matter Results from the XENON100 Experiment"}
Collar J. I., McKinsey D. N. Comments on «First Dark Matter Results from the XENON100 Experiment» // Eprint arXiv:1005.0838. 2010.

\bibitem{A Coherent Understanding of Low-Energy Nuclear Recoils in Liquid Xenon}
Sorensen P. A Coherent Understanding of Low-Energy Nuclear Recoils in Liquid Xenon // J. Cosmol. Astropart. Phys. 2010. Vol. 9. 033. 

\bibitem{Neutrino Detection with CLEAN}
McKinsey D. N., Coakley K. J. Neutrino Detection with CLEAN // Astropart. Phys. 2005. Vol. 22. P. 355. 

\bibitem{A Concept for a Dark Matter Detector Using Liquid Helium-4}
Guo W., McKinsey D. N. A Concept for a Dark Matter Detector Using Liquid Helium-4 // Eprint arXiv:1302.0534. 2013. 

\bibitem{A Survey of Energy Loss Calculations for Heavy Ions between 1 and 100 kev}
Mangiarotti A. et al. A Survey of Energy Loss Calculations for Heavy Ions between 1 and 100 kev // Nucl. Instrum. Meth. A. 2007. Vol. 580. P. 114. 

\bibitem{A Model of Nuclear Recoil Scintillation Efficiency in Noble Liquids}
Mei D.-M. et al. A Model of Nuclear Recoil Scintillation Efficiency in Noble Liquids // Astropart. Phys. 2008. Vol. 30. P. 12. 

\bibitem{Ionization Efficiency Study for Low Energy Nuclear Recoils in Germanium}
Barker D. et al. Ionization Efficiency Study for Low Energy Nuclear Recoils in Germanium // Eprint arXiv: 1304.6773. 2013. 

\bibitem{Quenching and Channeling of Nuclear Recoils in NaI[Tl]: Implications for Dark Matter Searches}
Collar J.I. Quenching and Channeling of Nuclear Recoils in NaI[Tl]: Implications for Dark Matter Searches // Eprint: arXiv:1302. 0796. 2013.

\bibitem{Scintillation Efficiency and Ionization Yield of Liquid Xenon for Monoenergetic Nuclear Recoils down to 4 keV}
Manzur A. et al. Scintillation Efficiency and Ionization Yield of Liquid Xenon for Monoenergetic Nuclear Recoils down to 4 keV // Phys. Rev. C. 2010. Vol. 81. 025808. 

\bibitem{Nuclear Recoil Scintillation and Ionisation Yields in Liquid Xenon from ZEPLIN-III Data}
Horn M. et al. Nuclear Recoil Scintillation and Ionisation Yields in Liquid Xenon from ZEPLIN-III Data // Phys. Lett. B. 2011. Vol. 705. P. 471. 

\bibitem{New Measurement of the Scintillation Efficiency of Low-Energy Nuclear Recoils in Liquid Xenon}
Plante G. et al. New Measurement of the Scintillation Efficiency of Low-Energy Nuclear Recoils in Liquid Xenon // Phys. Rev. C. 2011. Vol. 84. 045805. 

\bibitem{Measurement of Scintillation Efficiency for Nuclear Recoils in Liquid Argon}
Gastler D. et al. Measurement of Scintillation Efficiency for Nuclear Recoils in Liquid Argon // Phys. Rev. C. 2012. Vol. 85. 065811. 

\bibitem{Study of Nuclear Recoils in Liquid Argon with Monoenergetic Neutrons}
Regenfus C. et al. Study of Nuclear Recoils in Liquid Argon with Monoenergetic Neutrons // J. Phys.: Conf. Ser. 2012. Vol. 375. 012019. 

\bibitem{Scintillation Yield and Time Dependence from Electronic and Nuclear Recoils in Liquid Neon}
Lippincott W. H. et al. Scintillation Yield and Time Dependence from Electronic and Nuclear Recoils in Liquid Neon // Phys. Rev. C. 2012. Vol. 86. 015807. 


\end{thebibliography}

